---
title: "Factor Analysis"
output: html_notebook
---

#### Objective as per Work Break Down Structure 2.2

<li> Column by Column analysis is already done and the results can be obtained from https://docs.google.com/document/d/1eM_n3l7aFJWi6ryz_2_3750k1JmR-NseMxmHHHh-JaU/edit# </li>
<li> This notebook has to strictly used for HCA only. </li>
<li> All attemts has to be made to preserve all versions of dataset.</li>
<li> Camel Coding has to be followed.</li>
<li> Please add the relevant comments and indexes where ever required.</li>

The objective of this notebook is to cross-validate the number of components and the loadings in them.

#### Important Libraries
```{r}
library('gmodels')
library('psych')  # Procedures for Psychological, Psychometric, and Personality Research, used for factor analysis
library('caret')
library('corrplot')

```


## 1 Reading Data

```{r}
# Setting up the environment
rm(list = ls())
getwd()
data <- read.csv('../data/filtered_data.csv')  # please note our dataset is already scaled
data = subset(data, select = -c(X) ) # dropping X
dim(data)

colnames(data)



```


```{r}
#keeping only correlated variables

df_cor = findCorrelation(cor(data), cutoff=0.30)
hc= sort(df_cor)
correlated_data = data[, c(hc)]
dim(correlated_data)
```



```{r}

corrplot(cor(correlated_data), method="circle")
```


```{r}
#Correlated Data
#Bartlett’s test of sphericity
cortest.bartlett(cor(correlated_data), n=nrow(correlated_data))
#the Kaiser-Meyer-Olkin test
KMO(correlated_data)
```


### Performing FA
```{r}
#----4 Factors----------------------------------------------
fa_psych <- fa(correlated_data, nfactors=3, rotate = "promax")
print(fa_psych,cu=0.22,digits=2,sort=T)
fa.diagram(fa_psych,e.size=.035,digits=2, cut=0.10)

```

```{r}
colnames(fa_psych$loadings) <- c("facial_expression",
                                 "physical_strain",
                                 "work_strain")
```


```{r}
fa.diagram(fa_psych,e.size=.045,digits=2, cut=0.10)

```




# Parallel Analysis of Scree  plot
```{r}
fa.parallel.analysis<-fa.parallel(data,fm='minres',fa='fa')
```

