---
title: "Cluster Validation"
output: html_notebook
---

#### Objective as per Work Break Down Structure 3.1

<li> Column by Column analysis is already done and the results can be obtained from https://docs.google.com/document/d/1eM_n3l7aFJWi6ryz_2_3750k1JmR-NseMxmHHHh-JaU/edit# </li>
<li> This notebook has to strictly used for HCA only. </li>
<li> All attemts has to be made to preserve all versions of dataset.</li>
<li> Camel Coding has to be followed.</li>
<li> Please add the relevant comments and indexes where ever required.</li>

#### Important Libraries
```{r}
library(factoextra)
library(corrplot)
library(cluster)
library("clustertend")
library(grid)
library(clValid)
library(caret)
```


## 1 Reading Data

```{r}
# Setting up the environment
rm(list = ls())
getwd()
data <- read.csv('../data/pca_components.csv')  # please note our dataset is already scaled
data = subset(data, select = -c(X) ) # since two components are kind of same we will drop the second one
dim(data)
#data = scale(data)
colnames(data)



```

## Sampling of 10 % of data

```{r}
#set.seed(123)
#sample_data <- data[sample(nrow(data), 0.1*nrow(data)),]
#dim(sample_data)


#sample_first_four_compnents <- subset(sample_data, select =c('facial_expression','physical_strain','work_strain'))

```

## subsetting first three components
```{r}
first_three_component <- subset(data, select = c('PC1','PC2','PC3'))
```

### plotting dissimilarity distances
```{r}
fviz_dist(dist(first_three_component), show_labels = FALSE)+
labs(title = "Dissimilarity Distance")
```


### The K means with optimal clusters

```{r}
kmeans.model.k_3_scaled.only.3.components <- kmeans(first_three_component, 
                          centers = 2, 
                          iter.max = 10, 
                          nstart = 1000)
fviz_cluster(kmeans.model.k_3_scaled.only.3.components, first_three_component, ellipse.type = "norm")

```



```{r}
dissimilarity_distance <- dist(first_three_component, method = "euclidean")

# R base function hclust() can be used to create the hierarchical tree.
ward.hclust.model  <-  hclust(d = dissimilarity_distance, method = "ward.D2")
ward.hclust.model
```



```{r}

validation_data <- cbind(first_three_component, kmeans_cluster = kmeans.model.k_3_scaled.only.3.components$cluster)
```


```{r}
validation_data <- cbind(validation_data, h_cluster = cutree(ward.hclust.model, k = 2))
```



```{r}
typeof(validation_data)
validation_dataset<-as.data.frame(validation_data)
typeof(validation_dataset)
```


```{r}
#naming clusters correctly
validation_dataset$kmeans_cluster[validation_dataset$kmeans_cluster == 1] <- 'a'
validation_dataset$kmeans_cluster[validation_dataset$kmeans_cluster == 2] <- 'b'

validation_dataset$h_cluster[validation_dataset$h_cluster == 1] <- 'b'
validation_dataset$h_cluster[validation_dataset$h_cluster == 2] <- 'a'

```



```{r}
table(validation_dataset$kmeans_cluster, validation_dataset$h_cluster)
```



```{r}
confusionMatrix(table(validation_dataset$kmeans_cluster, validation_dataset$h_cluster))
```



```{r}
write.csv(validation_dataset, "../data/validation_data.csv")
```






```{r}
library(fpc)

cluster.stats(dissimilarity_distance, kmeans.model.k_3_scaled.only.3.components$cluster)
```


```{r}
cluster.stats(dissimilarity_distance, cutree(ward.hclust.model, k = 2))
```

