---
title: "Hierarchical K-Means Clustering: Optimize Clusters"
output: html_notebook
---


#### Objective as per Work Break Down Structure 3.1

<li> Column by Column analysis is already done and the results can be obtained from https://docs.google.com/document/d/1eM_n3l7aFJWi6ryz_2_3750k1JmR-NseMxmHHHh-JaU/edit# </li>
<li> This notebook has to strictly used for HCA only. </li>
<li> All attemts has to be made to preserve all versions of dataset.</li>
<li> Camel Coding has to be followed.</li>
<li> Please add the relevant comments and indexes where ever required.</li>

#### Important Libraries
```{r}
library(factoextra)
library(corrplot)
library(cluster)
library("clustertend")
library(grid)
library(NbClust)
```


## 1 Reading Data

```{r}
# Setting up the environment
rm(list = ls())
getwd()
data <- read.csv('../data/pca_components.csv')  # please note our dataset is already scaled
data = subset(data, select = -c(X) ) # since two components are kind of same we will drop the second one
dim(data)

colnames(data)



```

## Sampling of 10 % of data

```{r}
#set.seed(678)
#sample_data <- data[sample(nrow(data), 0.3*nrow(data)),]  # currently consdering 10% of sample data
#dim(sample_data)


#sample_first_four_compnents <- subset(sample_data, select =c('facial_expression','beauty_attributes','picture_quality_blurness','job_history'))

#dim(sample_first_four_compnents)
```


## subsetting data only three component
```{r}
only_three_component <- subset(data, select = c(PC1,PC2, PC3)) 
```


## hierarchical k-means clustering

<li>improving k-means results, using hkmeans</li>
__Algo__ <br>
<li>Compute hierarchical clustering and cut the tree into k-clusters</li>
<li>Compute the center (i.e the mean) of each cluster</li>
<li>Compute k-means by using the set of cluster centers (defined in step 2) as the initial cluster centers</li>
https://www.datanovia.com/en/lessons/hierarchical-k-means-clustering-optimize-clusters/


```{r}
hk.model_k2 <-hkmeans(only_three_component, 2)
```


```{r}
# Visualize the tree
fviz_dend(hk.model_k2, cex = 0.6, palette = "jco", 
          rect = TRUE, rect_border = "jco", rect_fill = TRUE)
```



```{r}
# Visualize the hkmeans final clusters
fviz_cluster(hk.model_k2, palette = "jco", repel = TRUE,
             ggtheme = theme_classic())
```


```{r}
fviz_cluster(hk.model_k2, only_three_component, ellipse.type = "norm")
```



```{r}
table(hk.model_k2$cluster)
```

```{r}
dissimilarity_distance <- dist(oonly_three_component, method = "euclidean")
library(fpc)

cluster.stats(dissimilarity_distance, hk.model_k2$cluster)
```

