---
title: "Cluster Interpretation"
output: html_notebook
---

#### Objective as per Work Break Down Structure 3.1

<li> Column by Column analysis is already done and the results can be obtained from https://docs.google.com/document/d/1eM_n3l7aFJWi6ryz_2_3750k1JmR-NseMxmHHHh-JaU/edit# </li>
<li> This notebook has to strictly used for HCA only. </li>
<li> All attemts has to be made to preserve all versions of dataset.</li>
<li> Camel Coding has to be followed.</li>
<li> Please add the relevant comments and indexes where ever required.</li>

#### Important Libraries
```{r}
library(factoextra)
library(corrplot)
library(cluster)
library("clustertend")
library(grid)
library(clValid)
library(caret)
library(DMwR)
```

## 1 Reading Data

```{r}
# Setting up the environment
rm(list = ls())
getwd()
original_data <- read.csv('filtered_data.csv')    # this is scaled data   :(
recovered_data <- read.csv('recovered_data.csv')  # this is unscaled data :) 
validation_data <- read.csv("validation_data.csv")

dim(recovered_data) 
dim(validation_data)
```



### join tables
```{r}
#merged_data <- merge(x=original_data,y=validation_data,by="X")
merged_data <- cbind(recovered_data,validation_data)
dim(merged_data)
```

### Selecting only desired columns , ie removing the PCA components and X

```{r}
mydata <- subset(merged_data, select = -c(X,PC1, PC2, PC3) )
mydata <- subset(mydata, select = -c(X) )

dim(mydata) # 48 data features  and 2 from clustering analysis  
```

### selecting only those who are identified into same clsuters by both
```{r}
final_data <- subset(mydata, mydata$kmeans_cluster == mydata$h_cluster)
dim(final_data) #25556 data points are corectly identified by both clustering technique

write.csv(final_data, "final_data_for_interpretation.csv")
```


### Aggregations
```{r}
aggregate(final_data, by = list(final_data$kmeans_cluster), mean)
```

